---
title: "Decision_tree"
output: html_document
---

# Import the packages
```{r}
library(dplyr)
library(caret) # for the confusion matrix 
library(rpart)
library(rpart.plot)
```


# Import train and test data

```{r}
train_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_train_data.csv", sep=";", dec=",")
test_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_test_data.csv", sep=";", dec=",")
```

```{r}
train_data$Class = as.factor(train_data$Class)
test_data$Class = as.factor(test_data$Class)
```

# Decision tree

## Without normalization
We build a decision tree with the unnormalized attributes
```{r}
options(repr.plot.width = 6, repr.plot.height = 5) # options for display of the tree

raisin_tree <- rpart(Class ~ Area +
                       MajorAxisLength +
                       MinorAxisLength +
                       Eccentricity +
                       ConvexArea +
                       Extent +
                       Perimeter,
                     data = train_data)     

prp(raisin_tree,      # Plot the decision tree
    space=4,          # (Formatting options chosen for notebook)
    split.cex = 1.5,
    nn.border.col=0)
```

```{r}
# Testing on the train data
predict_model<-predict(raisin_tree, new_data=train_data, type = "class")

confusionMatrix(predict_model, train_data$Class)
```

```{r}
# Testing on the test data
test_preds <- predict(raisin_tree,              
                      newdata=test_data,      
                      type="class") 

conf_matrix <-confusionMatrix(test_preds, test_data$Class)
conf_matrix
```


```{r}
accuracy_without_normalization_on_test_data <- conf_matrix[["overall"]][["Accuracy"]]
```


## With z-normalization
We build a decision tree with the z-normalized attributes
```{r}
options(repr.plot.width = 6, repr.plot.height = 5) 

raisin_tree_z_transformed <- rpart(Class ~ 
                                   z_transformed_Area +
                                   z_transformed_MajorAxisLength +
                                   z_transformed_MinorAxisLength +
                                   z_transformed_Eccentricity +
                                   z_transformed_ConvexArea +
                                   z_transformed_Extent +
                                   z_transformed_Perimeter,
                                 data = train_data)     


prp(raisin_tree_z_transformed,
    space=4,          
    split.cex = 1.5,
    nn.border.col=0)
```

```{r}
# Testing on the train data
predict_train_z_tranformed<-predict(raisin_tree_z_transformed, new_data=train_data, type = "class")

confusionMatrix(predict_train_z_tranformed, train_data$Class)
```

```{r}
# Testing on the test data
predict_test_z_tranformed <- predict(raisin_tree_z_transformed,              
                      newdata=test_data,      
                      type="class") 

conf_matrix <- confusionMatrix(predict_test_z_tranformed, test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```


## With z-log normalization
We build a decision tree with the z-log normalized attributes
```{r}
options(repr.plot.width = 6, repr.plot.height = 5)

raisin_tree_z_log_transformed <- rpart(Class ~ z_log_transformed_Area +
                                       z_log_transformed_MajorAxisLength +
                                       z_log_transformed_MinorAxisLength +
                                       z_log_transformed_Eccentricity +
                                       z_log_transformed_ConvexArea +
                                       z_log_transformed_Extent +
                                       z_log_transformed_Perimeter,
                                     data = train_data)     


prp(raisin_tree_z_log_transformed,
    space=4,
    split.cex = 1.5,
    nn.border.col=0)
```

```{r}
# Testing on the train data
predict_train_z_log_tranformed<-predict(raisin_tree_z_log_transformed,
                                        new_data=train_data,
                                        type = "class")

confusionMatrix(predict_train_z_log_tranformed, train_data$Class)
```

```{r}
# Testing on the test data
predict_test_z_log_tranformed <- predict(raisin_tree_z_log_transformed,           
                                         newdata=test_data,
                                         type="class") 

conf_matrix <- confusionMatrix(predict_test_z_log_tranformed, test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_log_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```


# Cross-Validation
We apply the k-fold cross validation

```{r}
data_cross_validation <- read.csv2("./dataset/data_transformed/data_for_cross_validation.csv", sep=";", dec=",")
data_cross_validation$Class = as.factor(data_cross_validation$Class)
```

```{r}
K <- max(data_cross_validation$k)
```

## Without normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- rpart(Class ~ Area +
                       MajorAxisLength +
                       MinorAxisLength +
                       Eccentricity +
                       ConvexArea +
                       Extent +
                       Perimeter,
                     data = data_cross_validation[data_cross_validation$k != i,])
  
  pred <- predict(model, newdata=data_cross_validation[data_cross_validation$k == i,],type="class") 

  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, pred)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_without_normalization <- mean_accuracy
```

## With Z-normalization
```{r}
error_list <- c()
for (i in 1:K){
  model <- rpart(Class ~ z_transformed_Area +
                   z_transformed_MajorAxisLength +
                   z_transformed_MinorAxisLength +
                   z_transformed_Eccentricity +
                   z_transformed_ConvexArea +
                   z_transformed_Extent +
                   z_transformed_Perimeter,
                 data = data_cross_validation[data_cross_validation$k != i,])     
    
  
  pred <- predict(model, newdata=data_cross_validation[data_cross_validation$k == i,],type="class") 

  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, pred)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_normalization <- mean_accuracy
```

## With Z-log normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- rpart(Class ~ z_log_transformed_Area +
                   z_log_transformed_MajorAxisLength +
                   z_log_transformed_MinorAxisLength +
                   z_log_transformed_Eccentricity +
                   z_log_transformed_ConvexArea +
                   z_log_transformed_Extent +
                   z_log_transformed_Perimeter,
                 data = data_cross_validation[data_cross_validation$k != i,])     
    
  
  pred <- predict(model, newdata=data_cross_validation[data_cross_validation$k == i,],type="class") 

  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, pred)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_log_normalization <- mean_accuracy
```

# Write the results into a file
We write all the results into a file so that we can do a summary in the evaluation_phase.Rmd file

```{r}
decision_tree_results <- c(accuracy_without_normalization_on_test_data,
                   accuracy_with_z_normalization_on_test_data,
                   accuracy_with_z_log_normalization_on_test_data,
                   accuracy_k_fold_crossvalidation_without_normalization,
                   accuracy_k_fold_crossvalidation_with_z_normalization,
                   accuracy_k_fold_crossvalidation_with_z_log_normalization )

name <- c("without normalization on test data",
          "with z normalization on test data",
          "with z log normalization on test data",
          "k fold crossvalidation without normalization",
          "k fold crossvalidation with z normalization",
          "k fold crossvalidation with z log normalization" )

df <- data.frame(name, decision_tree_results)
```

```{r}
df
```
```{r}
write.csv2(df, file="./dataset/results/decision_tree.csv", row.names = FALSE)
```

