---
title: "knn"
output: html_document
---

# Import the packages
```{r}
library(tidyverse)
library(dplyr)
library(class)
library(caret)
```

# Import train and test data

```{r}
train_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_train_data.csv", sep=";", dec=",")
test_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_test_data.csv", sep=";", dec=",")
```

```{r}
train_data$Class = as.factor(train_data$Class)
test_data$Class = as.factor(test_data$Class)
```

# K-nearest neighbor

```{r}
train_target_category <- train_data[, ncol(train_data)]
test_target_category <- test_data[, ncol(test_data)]
```

## Without normalization 
We build a knn with the unnormalized attributes
```{r}
# Columns that will be considered during the classification
columns_without_normalization = c("Area",
                                  "MajorAxisLength",
                                  "MinorAxisLength",
                                  "Eccentricity",
                                  "ConvexArea",
                                  "Extent",
                                  "Perimeter")
```

```{r}
train_data_without_normalization <- train_data %>% select(columns_without_normalization)
test_data_without_normalization <- test_data %>% select(columns_without_normalization)
```

```{r}
# Predict on the train data 
pr_train <- knn(train_data_without_normalization,train_data_without_normalization,cl=train_target_category,k=3)
```

```{r}
# Predict on the test data
pr_test <- knn(train_data_without_normalization,test_data_without_normalization,cl=train_target_category,k=3)
```

```{r}
confusionMatrix(pr_train,train_target_category)
```

```{r}
conf_matrix <- confusionMatrix(pr_test,test_target_category)
conf_matrix
```

```{r}
accuracy_without_normalization_on_test_data <- conf_matrix[["overall"]][["Accuracy"]]
```

## With z-normalization
We build a knn with the z-normalized attributes
```{r}
# Columns that will be considered during the classification
columns_with_z_normalization = c("z_transformed_Area",
                                 "z_transformed_MajorAxisLength",
                                 "z_transformed_MinorAxisLength",
                                 "z_transformed_Eccentricity",
                                 "z_transformed_ConvexArea",
                                 "z_transformed_Extent",
                                 "z_transformed_Perimeter")
```

```{r}
train_data_with_z_normalization <- train_data %>% select(columns_with_z_normalization)
test_data_with_z_normalization <- test_data %>% select(columns_with_z_normalization)
```

```{r}
# Predict on the train data 
pr_train <- knn(train_data_with_z_normalization,train_data_with_z_normalization,cl=train_target_category,k=3)
```

```{r}
# Predict on the test data
pr_test <- knn(train_data_with_z_normalization,test_data_with_z_normalization,cl=train_target_category,k=3)
```

```{r}
confusionMatrix(pr_train,train_target_category)
```

```{r}
conf_matrix <- confusionMatrix(pr_test,test_target_category)
conf_matrix
```

```{r}
accuracy_with_z_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

## With z-log normalisation
We build a knn with the z-log normalized attributes
```{r}
# Columns that will be considered during the classification
columns_with_z_log_normalization = c("z_log_transformed_Area",
                                     "z_log_transformed_MajorAxisLength",
                                     "z_log_transformed_MinorAxisLength",
                                     "z_log_transformed_Eccentricity",
                                     "z_log_transformed_ConvexArea",
                                     "z_log_transformed_Extent",
                                     "z_log_transformed_Perimeter")
```

```{r}
train_data_with_z_log_normalization <- train_data %>% select(columns_with_z_log_normalization)
test_data_with_z_log_normalization <- test_data %>% select(columns_with_z_log_normalization)
```

```{r}
# Predict on the train data 
pr_train <- knn(train_data_with_z_log_normalization,train_data_with_z_log_normalization,cl=train_target_category,k=3)
```

```{r}
# Predict on the test data
pr_test <- knn(train_data_with_z_log_normalization,test_data_with_z_log_normalization,cl=train_target_category,k=3)
```

```{r}
confusionMatrix(pr_train,train_target_category)
```

```{r}
conf_matrix <- confusionMatrix(pr_test,test_target_category)
conf_matrix
```


```{r}
accuracy_with_z_log_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

# Cross-Validation

```{r}
data_cross_validation <- read.csv2("./dataset/data_transformed/data_for_cross_validation.csv", sep=";", dec=",")
data_cross_validation$Class = as.factor(data_cross_validation$Class)
```

```{r}
K <- max(data_cross_validation$k)
```

## Without normalization


```{r}
error_list <- c()
for (i in 1:K){
  train_data_cross_validation <- data_cross_validation[data_cross_validation$k != i,]
  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  train_target_category <- train_data_cross_validation[, ncol(train_data_cross_validation)-1]
  test_target_category <- test_data_cross_validation[, ncol(test_data_cross_validation)-1]
  
  train_data_cross_validation <- train_data_cross_validation %>% select(columns_without_normalization)
  test_data_cross_validation <- test_data_cross_validation %>% select(columns_without_normalization)
  
  pr_test <- knn(train_data_cross_validation, test_data_cross_validation, cl=train_target_category, k=3)
  
  conf_mat <- confusionMatrix(pr_test, test_target_category)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```
```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_without_normalization <- mean_accuracy
```

## With Z-normalization

```{r}
error_list <- c()
for (i in 1:K){
  train_data_cross_validation <- data_cross_validation[data_cross_validation$k != i,]
  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  train_target_category <- train_data_cross_validation[, ncol(train_data_cross_validation)-1]
  test_target_category <- test_data_cross_validation[, ncol(test_data_cross_validation)-1]
  
  train_data_cross_validation <- train_data_cross_validation %>% select(columns_with_z_normalization)
  test_data_cross_validation <- test_data_cross_validation %>% select(columns_with_z_normalization)
  
  pr_test <- knn(train_data_cross_validation, test_data_cross_validation, cl=train_target_category, k=3)
  
  conf_mat <- confusionMatrix(pr_test, test_target_category)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_normalization <- mean_accuracy
```

## With Z-log normalization

```{r}
error_list <- c()
for (i in 1:K){
  train_data_cross_validation <- data_cross_validation[data_cross_validation$k != i,]
  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  train_target_category <- train_data_cross_validation[, ncol(train_data_cross_validation)-1]
  test_target_category <- test_data_cross_validation[, ncol(test_data_cross_validation)-1]
  
  train_data_cross_validation <- train_data_cross_validation %>% select(columns_with_z_log_normalization)
  test_data_cross_validation <- test_data_cross_validation %>% select(columns_with_z_log_normalization)
  
  pr_test <- knn(train_data_cross_validation, test_data_cross_validation, cl=train_target_category, k=3)
  
  conf_mat <- confusionMatrix(pr_test, test_target_category)
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```

```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_log_normalization <- mean_accuracy
```

# Write the results into a file
We write all the results into a file so that we can do a summary in the evaluation_phase.Rmd file

```{r}
knn <- c(accuracy_without_normalization_on_test_data,
                   accuracy_with_z_normalization_on_test_data,
                   accuracy_with_z_log_normalization_on_test_data,
                   accuracy_k_fold_crossvalidation_without_normalization,
                   accuracy_k_fold_crossvalidation_with_z_normalization,
                   accuracy_k_fold_crossvalidation_with_z_log_normalization )

name <- c("without normalization on test data",
          "with z normalization on test data",
          "with z log normalization on test data",
          "k fold crossvalidation without normalization",
          "k fold crossvalidation with z normalization",
          "k fold crossvalidation with z log normalization" )

df <- data.frame(name, knn)
```

```{r}
df
```

```{r}
write.csv2(df, file="./dataset/results/knn.csv", row.names = FALSE)
```



