---
title: "Logistic_regression"
output: html_document
---

# Import the packages
```{r}
library(tidyverse)
library(dplyr)
library(caret)
```


# Import train and test data

```{r}
train_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_train_data.csv", sep=";", dec=",")
test_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_test_data.csv", sep=";", dec=",")
```

```{r}
train_data$Class = as.factor(train_data$Class)
test_data$Class = as.factor(test_data$Class)
```

# Logistic regression

## Without normalization
We build a logistic regression with the unnormalized attributes
```{r}
model_withtout_normalization <- glm(Class ~ Area +
                                      MajorAxisLength +
                                      MinorAxisLength +
                                      Eccentricity +
                                      ConvexArea +
                                      Extent +
                                      Perimeter,
                                    family=binomial(link='logit'),
                                    data=train_data)

summary(model_withtout_normalization)
```

```{r}
probabs_without_normalization <- predict(model_withtout_normalization, train_data, type='response') 

preds_without_normalization <- ifelse(probabs_without_normalization > 0.5, "Kecimen", "Besni")

confusionMatrix(factor(preds_without_normalization), train_data$Class)
```

```{r}
probabs_without_normalization <- predict(model_withtout_normalization, test_data, type='response') 

preds_without_normalization <- ifelse(probabs_without_normalization > 0.5, "Kecimen", "Besni")

conf_matrix <- confusionMatrix(factor(preds_without_normalization), test_data$Class)
conf_matrix
```

```{r}
accuracy_without_normalization_on_test_data <- conf_matrix[["overall"]][["Accuracy"]]
```

## With z-normalization
We build a logistic regression with the z-normalized attributes
```{r}
model_with_z_normalization <-  glm(Class ~ z_transformed_Area +
                                     z_transformed_MajorAxisLength +
                                     z_transformed_MinorAxisLength +
                                     z_transformed_Eccentricity +
                                     z_transformed_ConvexArea +
                                     z_transformed_Extent +
                                     z_transformed_Perimeter,
                                   family=binomial(link='logit'),
                                   data=train_data)

summary(model_with_z_normalization)
```

```{r}
probabs_with_z_normalization <- predict(model_with_z_normalization, train_data, type='response') 

preds_with_z_normalization <- ifelse(probabs_with_z_normalization > 0.5,  "Kecimen", "Besni")

confusionMatrix(factor(preds_with_z_normalization), train_data$Class)
```

```{r}
probabs_with_z_normalization <- predict(model_with_z_normalization, test_data, type='response') 

preds_with_z_normalization <- ifelse(probabs_with_z_normalization > 0.5,  "Kecimen", "Besni")

conf_matrix <- confusionMatrix(factor(preds_with_z_normalization), test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

## With z-log normalization
We build a logistic regression with the z-log normalized attributes
```{r}
model_with_z_log_normalization <- glm(Class ~ z_log_transformed_Area +
                                        z_log_transformed_MajorAxisLength +
                                        z_log_transformed_MinorAxisLength +
                                        z_log_transformed_Eccentricity +
                                        z_log_transformed_ConvexArea +
                                        z_log_transformed_Extent +
                                        z_log_transformed_Perimeter,
                                      family=binomial(link='logit'),
                                      data=train_data)

summary(model_with_z_log_normalization)
```

```{r}
probabs_with_z_log_normalization <- predict(model_with_z_log_normalization, train_data, type='response') 

preds_with_z_log_normalization <- ifelse(probabs_with_z_log_normalization > 0.5,  "Kecimen", "Besni")

confusionMatrix(factor(preds_with_z_log_normalization), train_data$Class)
```

```{r}
probabs_with_z_log_normalization <- predict(model_with_z_log_normalization, test_data, type='response') 

preds_with_z_log_normalization <- ifelse(probabs_with_z_log_normalization > 0.5,  "Kecimen", "Besni")

conf_matrix <- confusionMatrix(factor(preds_with_z_log_normalization), test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_log_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

# Cross-Validation

```{r}
data_cross_validation <- read.csv2("./dataset/data_transformed/data_for_cross_validation.csv", sep=";", dec=",")
data_cross_validation$Class = as.factor(data_cross_validation$Class)
```

```{r}
K <- max(data_cross_validation$k)
```

## Without normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- glm(Class ~ Area +
                 MajorAxisLength +
                 MinorAxisLength +
                 Eccentricity +
                 ConvexArea +
                 Extent +
                 Perimeter,
               family=binomial(link='logit'),
               data=data_cross_validation[data_cross_validation$k != i,])

  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  probabs <- predict(model, test_data_cross_validation, type='response') 
  
  preds <- ifelse(probabs > 0.5,  "Kecimen", "Besni")
  
  conf_mat <- confusionMatrix(test_data_cross_validation$Class, factor(preds))
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_without_normalization <- mean_accuracy
```

## With Z-normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- glm(Class ~ z_transformed_Area +
                 z_transformed_MajorAxisLength +
                 z_transformed_MinorAxisLength +
                 z_transformed_Eccentricity +
                 z_transformed_ConvexArea +
                 z_transformed_Extent +
                 z_transformed_Perimeter,
               family=binomial(link='logit'),
               data=data_cross_validation[data_cross_validation$k != i,])

  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  probabs <- predict(model, test_data_cross_validation, type='response') 
  
  preds <- ifelse(probabs > 0.5, "Kecimen", "Besni")
  
  conf_mat <- confusionMatrix(factor(preds), factor(test_data_cross_validation$Class))
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_normalization <- mean_accuracy
```

## With Z-log normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- glm(Class ~ z_log_transformed_Area +
                 z_log_transformed_MajorAxisLength +
                 z_log_transformed_MinorAxisLength +
                 z_log_transformed_Eccentricity +
                 z_log_transformed_ConvexArea +
                 z_log_transformed_Extent +
                 z_log_transformed_Perimeter,
               family=binomial(link='logit'),
               data = data_cross_validation[data_cross_validation$k != i,])

  test_data_cross_validation <- data_cross_validation[data_cross_validation$k == i,]
  
  probabs <- predict(model, test_data_cross_validation, type='response') 
  
  preds <- ifelse(probabs > 0.5,  "Kecimen", "Besni")
  
  conf_mat <- confusionMatrix(factor(preds), factor(test_data_cross_validation$Class))
  
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```

```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_log_normalization <- mean_accuracy
```

# Write the results into a file
We write all the results into a file so that we can do a summary in the evaluation_phase.Rmd file

```{r}
logistic_regression_results <- c(accuracy_without_normalization_on_test_data,
                   accuracy_with_z_normalization_on_test_data,
                   accuracy_with_z_log_normalization_on_test_data,
                   accuracy_k_fold_crossvalidation_without_normalization,
                   accuracy_k_fold_crossvalidation_with_z_normalization,
                   accuracy_k_fold_crossvalidation_with_z_log_normalization )

name <- c("without normalization on test data",
          "with z normalization on test data",
          "with z log normalization on test data",
          "k fold crossvalidation without normalization",
          "k fold crossvalidation with z normalization",
          "k fold crossvalidation with z log normalization" )

df <- data.frame(name, logistic_regression_results)
```

```{r}
df
```

```{r}
write.csv2(df, file="./dataset/results/logistic_regression.csv", row.names = FALSE)
```