---
title: "Neural Network"
output: html_document
---

# Import the packages
```{r}
library(dplyr)
library(neuralnet)
source("./tools/data_modelling_functions.R")
```


# Import train and test data

```{r}
train_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_train_data.csv", sep=";", dec=",")
test_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_test_data.csv", sep=";", dec=",")
```

```{r}
train_data$Class = as.factor(train_data$Class)
test_data$Class = as.factor(test_data$Class)
```

# Neural network

```{r}
set.seed(124)
```

## Without normalization
We build a neural network with the unnormalized attributes
```{r}
columns_without_normalization <- c("Area","MajorAxisLength","MinorAxisLength","Eccentricity","ConvexArea","Extent","Perimeter", "Class")

train_data_without_normalization <- train_data %>% select(columns_without_normalization)
```


```{r}
nn = neuralnet(Class ~ Area +
                 MajorAxisLength +
                 MinorAxisLength +
                 Eccentricity +
                 ConvexArea +
                 Extent +
                 Perimeter,
             data=train_data, hidden=c(2, 2), act.fct = "logistic", linear.output = FALSE, stepmax = 1e7)
```


```{r}
plot(nn)
```

```{r}
labels <- c("Kecimen", "Besni")
```

```{r}
pred <- predict(nn, test_data, labels)
```

```{r}
pred[["conf_matrix"]]
```

```{r}
pred[["acccuracy"]]
```

```{r}
pred <- predict(nn, test_data, labels)
```

```{r}
pred[["conf_matrix"]]
```

```{r}
accuracy_without_normalization_on_test_data <- pred[["acccuracy"]]
accuracy_without_normalization_on_test_data
```


## With Z-normalization
We build a neural network with the z-normalized attributes

```{r}
nn_z_norm=neuralnet(Class ~ z_transformed_Area +
                        z_transformed_MajorAxisLength +
                        z_transformed_MinorAxisLength +
                        z_transformed_Eccentricity +
                        z_transformed_ConvexArea +
                        z_transformed_Extent +
                        z_transformed_Perimeter,
             data=train_data, hidden=c(2,2), act.fct = "logistic", linear.output = FALSE, stepmax = 1e7)
```


```{r}
plot(nn_z_norm)
```


```{r}
pred <- predict(nn_z_norm, train_data, labels)
```

```{r}
pred[["conf_matrix"]]
```

```{r}
pred[["acccuracy"]]
```


```{r}
pred <- predict(nn_z_norm, test_data, labels)
```


```{r}
pred[["conf_matrix"]]
```

```{r}
accuracy_with_z_normalization_on_test_data <- pred[["acccuracy"]]
accuracy_with_z_normalization_on_test_data
```


## With Z-log normalisation
We build a neural network with the z-log normalized attributes

```{r}
nn_z_log_norm=neuralnet(Class ~ z_log_transformed_Area +
                          z_log_transformed_MajorAxisLength +
                          z_log_transformed_MinorAxisLength +
                          z_log_transformed_Eccentricity +
                          z_log_transformed_ConvexArea +
                          z_log_transformed_Extent +
                          z_log_transformed_Perimeter,
                        data=train_data, hidden=c(2,2), act.fct = "logistic", linear.output = FALSE, stepmax=1e7)
```


```{r}
plot(nn_z_log_norm)
```


```{r}
pred <- predict(nn_z_log_norm, train_data, labels)
```

```{r}
pred[["conf_matrix"]]
```

```{r}
pred[["acccuracy"]]
```

```{r}
pred <- predict(nn_z_log_norm, test_data, labels)
```


```{r}
pred[["conf_matrix"]]
```

```{r}
accuracy_with_z_log_normalization_on_test_data <- pred[["acccuracy"]]
accuracy_with_z_log_normalization_on_test_data
```


# Cross-Validation

```{r}
data_cross_validation <- read.csv2("./dataset/data_transformed/data_for_cross_validation.csv", sep=";", dec=",")
data_cross_validation$Class = as.factor(data_cross_validation$Class)
```

```{r}
K <- max(data_cross_validation$k)
```


## Without normalization


```{r}
error_list <- c()
for (i in 1:K){
  model <- neuralnet(Class ~ Area +
                       MajorAxisLength +
                       MinorAxisLength +
                       Eccentricity +
                       ConvexArea +
                       Extent +
                       Perimeter,
                     data=data_cross_validation[data_cross_validation$k != i,],
                     hidden=c(2, 2),
                     act.fct = "logistic",
                     linear.output = FALSE,
                     stepmax = 1e7)
  
  pred <- predict(model, data_cross_validation[data_cross_validation$k == i,], labels)
  misclassification_rate <- 1- pred[["acccuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```
    
```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_without_normalization <- mean_accuracy
```


## With Z-normalization


```{r}
error_list <- c()
for (i in 1:K){
  model <- neuralnet(Class ~ z_transformed_Area +
                       z_transformed_MajorAxisLength +
                       z_transformed_MinorAxisLength +
                       z_transformed_Eccentricity +
                       z_transformed_ConvexArea +
                       z_transformed_Extent +
                       z_transformed_Perimeter,
                     data=data_cross_validation[data_cross_validation$k != i,],
                     hidden=c(2, 2),
                     act.fct = "logistic",
                     linear.output = FALSE,
                     stepmax = 1e7)
  
  pred <- predict(model, data_cross_validation[data_cross_validation$k == i,], labels)
  misclassification_rate <- 1- pred[["acccuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_normalization <- mean_accuracy
```


## With Z-log normalization


```{r}
error_list <- c()
for (i in 1:K){
  model <- neuralnet(Class ~ z_log_transformed_Area +
                       z_log_transformed_MajorAxisLength +
                       z_log_transformed_MinorAxisLength +
                       z_log_transformed_Eccentricity +
                       z_log_transformed_ConvexArea +
                       z_log_transformed_Extent +
                       z_log_transformed_Perimeter,
                     data=data_cross_validation[data_cross_validation$k != i,],
                     hidden=c(2, 2),
                     act.fct = "logistic",
                     linear.output = FALSE,
                     stepmax = 1e7)
  
  pred <- predict(model, data_cross_validation[data_cross_validation$k == i,], labels)
  misclassification_rate <- 1- pred[["acccuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_log_normalization <- mean_accuracy
```


# Write the results into a file
We write all the results into a file so that we can do a summary in the evaluation_phase.Rmd file

```{r}
random_forest_results <- c(accuracy_without_normalization_on_test_data,
                   accuracy_with_z_normalization_on_test_data,
                   accuracy_with_z_log_normalization_on_test_data,
                   accuracy_k_fold_crossvalidation_without_normalization,
                   accuracy_k_fold_crossvalidation_with_z_normalization,
                   accuracy_k_fold_crossvalidation_with_z_log_normalization )

name <- c("without normalization on test data",
          "with z normalization on test data",
          "with z log normalization on test data",
          "k fold crossvalidation without normalization",
          "k fold crossvalidation with z normalization",
          "k fold crossvalidation with z log normalization" )

df <- data.frame(name, random_forest_results)
```

```{r}
df
```

```{r}
write.csv2(df, file="./dataset/results/neural_network.csv", row.names = FALSE)
```

















