---
title: "Support vector machines"
output: html_document
---

# Import the packages
```{r}
library(e1071)
library(caret) # for the confusion matrix
```


# Import train and test data

```{r}
train_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_train_data.csv", sep=";", dec=",")
test_data <- read.csv2("./dataset/data_transformed/Raisin_transformed_test_data.csv", sep=";", dec=",")
```

```{r}
train_data$Class = as.factor(train_data$Class)
test_data$Class = as.factor(test_data$Class)
```

# Support Vector Machines (SVMs)

## Without normalization
We build a svm with the unnormalized attributes
```{r}
svm_model <- svm(Class ~ Area +
             MajorAxisLength +
             MinorAxisLength +
             Eccentricity +
             ConvexArea +
             Extent +
             Perimeter,
           data = train_data,
           type = 'C-classification',
           kernel = 'radial')
svm_model
```

```{r}
# prediction with training data
predict_train_data <- predict(svm_model, newdata = train_data)
confusionMatrix(predict_train_data, train_data$Class)
```

```{r}
# prediction with test data
predict_test_data <- predict(svm_model, test_data)
conf_matrix <- confusionMatrix(predict_test_data, test_data$Class)
conf_matrix
```

```{r}
accuracy_without_normalization_on_test_data <- conf_matrix[["overall"]][["Accuracy"]]
```

## With Z-normalization
We build a svm with the z-normalized attributes
```{r}
svm_model_z_normalization <- svm(Class ~ z_transformed_Area +
                                   z_transformed_MajorAxisLength +
                                   z_transformed_MinorAxisLength +
                                   z_transformed_Eccentricity +
                                   z_transformed_ConvexArea +
                                   z_transformed_Extent +
                                   z_transformed_Perimeter,
                                 data=train_data,
                                 type = 'C-classification',
                                 kernel = 'radial')
print(svm_model_z_normalization)
```

```{r}
# prediction with training data
predict_train_z_normalization <- predict(svm_model_z_normalization, train_data)
confusionMatrix(predict_train_z_normalization, train_data$Class)
```

```{r}
# prediction with test data
predict_test_data_z_normalization <- predict(svm_model_z_normalization, test_data)
conf_matrix <- confusionMatrix(predict_test_data_z_normalization, test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

## With Z-log normalization
We build a svm with the z-log normalized attributes
```{r}
svm_model_z_log_normalization <- svm(Class ~ z_log_transformed_Area +
                                                z_log_transformed_MajorAxisLength +
                                                z_log_transformed_MinorAxisLength +
                                                z_log_transformed_Eccentricity +
                                                z_log_transformed_ConvexArea +
                                                z_log_transformed_Extent +
                                                z_log_transformed_Perimeter,
                                              data=train_data,
                                              type = 'C-classification',
                                              kernel = 'radial')

print(svm_model_z_log_normalization)
```

```{r}
# prediction with training data
predict_train_z_log_normalization <- predict(svm_model_z_log_normalization, train_data)
confusionMatrix(predict_train_z_log_normalization, train_data$Class)
```

```{r}
# prediction with test data
predict_test_data_z_Log_normalization <- predict(svm_model_z_log_normalization, test_data)
conf_matrix <- confusionMatrix(predict_test_data_z_Log_normalization, test_data$Class)
conf_matrix
```

```{r}
accuracy_with_z_log_normalization_on_test_data <-conf_matrix[["overall"]][["Accuracy"]]
```

# Cross-Validation

```{r}
data_cross_validation <- read.csv2("./dataset/data_transformed/data_for_cross_validation.csv", sep=";", dec=",")
data_cross_validation$Class = as.factor(data_cross_validation$Class)
```

```{r}
K <- max(data_cross_validation$k)
```


## Without normalization

```{r}
error_list <- c()
for (i in 1:K){
  model <- svm(Class ~ Area +
                 MajorAxisLength +
                 MinorAxisLength +
                 Eccentricity +
                 ConvexArea +
                 Extent +
                 Perimeter,
               data = data_cross_validation[data_cross_validation$k != i,],
               type = 'C-classification',
               kernel = 'radial')

  predict_test_data <- predict(model, data_cross_validation[data_cross_validation$k == i,])
  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, predict_test_data)
    
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```


```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_without_normalization <- mean_accuracy
```

## With Z-normalization


```{r}
error_list <- c()
for (i in 1:K){
  model <- svm(Class ~ z_transformed_Area +
                 z_transformed_MajorAxisLength +
                 z_transformed_MinorAxisLength +
                 z_transformed_Eccentricity +
                 z_transformed_ConvexArea +
                 z_transformed_Extent +
                 z_transformed_Perimeter,
               data = data_cross_validation[data_cross_validation$k != i,],
               type = 'C-classification',
               kernel = 'radial')

  predict_test_data <- predict(model, data_cross_validation[data_cross_validation$k == i,])
  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, predict_test_data)
    
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```

```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_normalization <- mean_accuracy
```

## With Z-log normalization


```{r}
error_list <- c()
for (i in 1:K){
  model <- svm(Class ~ z_log_transformed_Area +
                 z_log_transformed_MajorAxisLength +
                 z_log_transformed_MinorAxisLength +
                 z_log_transformed_Eccentricity +
                 z_log_transformed_ConvexArea +
                 z_log_transformed_Extent +
                 z_log_transformed_Perimeter,
               data = data_cross_validation[data_cross_validation$k != i,],
               type = 'C-classification',
               kernel = 'radial')

  predict_test_data <- predict(model, data_cross_validation[data_cross_validation$k == i,])
  conf_mat <- confusionMatrix(data_cross_validation[data_cross_validation$k == i,]$Class, predict_test_data)
    
  misclassification_rate <- 1 - conf_mat[["overall"]][["Accuracy"]]
  error_list <- c(error_list, misclassification_rate)
}

error_list
```

```{r}
mean(error_list)
```

```{r}
mean_accuracy <- 1 - mean(error_list)
mean_accuracy
```

```{r}
accuracy_k_fold_crossvalidation_with_z_log_normalization <- mean_accuracy
```


# Write the results into a file
We write all the results into a file so that we can do a summary in the evaluation_phase.Rmd file

```{r}
support_vector_machines_results <- c(accuracy_without_normalization_on_test_data,
                   accuracy_with_z_normalization_on_test_data,
                   accuracy_with_z_log_normalization_on_test_data,
                   accuracy_k_fold_crossvalidation_without_normalization,
                   accuracy_k_fold_crossvalidation_with_z_normalization,
                   accuracy_k_fold_crossvalidation_with_z_log_normalization )

name <- c("without normalization on test data",
          "with z normalization on test data",
          "with z log normalization on test data",
          "k fold crossvalidation without normalization",
          "k fold crossvalidation with z normalization",
          "k fold crossvalidation with z log normalization" )

df <- data.frame(name, support_vector_machines_results)
```

```{r}
df
```

```{r}
write.csv2(df, file="./dataset/results/support_vector_machines.csv", row.names = FALSE)
```